Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
I think I fixed the duplicate data issue

# Set paths depending on machine Beas or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}else{
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

Clean_Results <- Results_Data %>% 
  filter(is.na(Trans_Index)) %>% 
  select(1:5)

length(unique(Clean_Results$TaxonKey))

head(Clean_Results)
```

@@

TenFifty <- Clean_Results %>% 
  filter(Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75
         ) %>% 
  group_by(Name=Country_Territory,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
    ) 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))
# 
# head(World_EEZs)

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(TenFifty, by ="Name") #%>%
  # filter(!is.na(n_trans)) #%>%
  # st_transform(crs = 3832)

@@

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_trans)) +
  scale_fill_gradientn(colours = pal) +
  ggtheme_map()

ggsave("R2_100_25_Fine_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@

```{r, Trans_Results, eval = F, echo = F}
```

>>>>

# Set paths depending on machine Beas or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}else{
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

@@

TenFifty <- Non_duplicate_Data %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  group_by(Territory1=fishing_entity,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
    ) %>% 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

# The path
path_world <- paste("~/Documents/UBC/Oceans_Project/Distribution/Data/Spatial/World_EEZ_v9_20161021",sep="")
# #The File
fnam_world <- "eez_boundaries.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))
# 
head(World_EEZs)

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
  left_join(TenFifty, by ="Name") %>%
  filter(!is.na(n_Trans_Spp)) #%>%
  # st_transform(crs = 3832)

@@

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_Trans_Spp)) +
  scale_fill_gradientn(colours = pal) +
  ggtheme_map()

ggsave("MI_100_TI_all_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@

```{r, SOM_Trans_Results, eval = F, echo = F}

Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv") %>% 
  filter(!is.na(Country_Territory))

sau_eez_fes <- read.csv("~/Desktop/sau_eez_fes.csv")

EEZID_D <- readxl::read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")

# Trying to fix EEZ problem...

sau_eez_fes <-sau_eez_fes %>% 
rename(EEZID = eez_id)

eez_list <- EEZID_D %>% 
  rename(Country_Territory=Name)

xx <- Clean_Results %>% 
  left_join(eez_list,
            by = "Country_Territory") %>% 
  left_join(sau_eez_fes,
            by = "EEZID")

Neighbord_Territory_T <- Clean_Results %>% 
  group_by(Neighbor_Territory) %>% 
  summarise() %>% 
  left_join(eez_list_n,
            by = "Neighbor_Territory") %>% 
  left_join(sau_eez_fes,
            by = "EEZID") %>% 
  select(Neighbor_Territory,neighbor_entity = fishing_entity)

Non_duplicate_Data <- xx %>%   
  left_join(Neighbord_Territory_T,
              by ="Neighbor_Territory") %>% 
  mutate(
    fishing_entity = ifelse(is.na(fishing_entity),paste(Country_Territory),paste(fishing_entity)),
    Same_Nation = ifelse(fishing_entity==neighbor_entity,paste("Yes"),"No")
  ) %>% 
  filter(Same_Nation == "No")

write.csv(Non_duplicate_Data,
          "New_Clean_Results.csv")
